Low-Cost Data Deduplication for Virtual Machine Backup in Cloud Storage

### 2013-12-10 batchdedup/scheduling.tex
added a representative histogram for one of the clusters

\section{Round Scheduling}
\label{sect:scheduling}
The naive way to take advantage of the efficiency of batch processing is to
schedule all the work to be done in one round.  
% This works well if all of the
% data being backed up are only copies, e.g. a separate backup system which data
% is sent to over the network. 
However, in our case we are backing up the
live virtual disks, thus such single round backup presents several problems
in our synchronous approach.
This first is that in order to preserve a consistent view of VM images, we apply
Copy-on-Write (CoW) to protect the dirty segments against incoming disk writes during 
the backup period of stage 1 and 2.
Previous studies have shown that as much as 8\% or even more of total capacity must be reserved for
CoW \cite{EMCIncrementalDataChanges}, while the actual cost of CoW is a factor of the
data size, the write rate, and duration of CoW protection.
The second problem is that a single round backup brings the highest cost of CoW
because of the workload in stage 1a is imbalanced,
causing machines with small VMs to wait while CoW protection is turned on.
Thus we must minimize the duration that a given VM is undergoing CoW protection.

>>>>

\section{Round Scheduling}
\label{sect:scheduling}
The naive way to take advantage of the efficiency of batch processing is to
schedule all the work to be done in one round.  
% This works well if all of the
% data being backed up are only copies, e.g. a separate backup system which data
% is sent to over the network. 
However, in our case we are backing up the
live virtual disks, thus such single round backup presents several problems
in our synchronous approach.
This first is that in order to preserve a consistent view of VM images, we apply
Copy-on-Write (CoW) to protect the dirty segments against incoming disk writes during 
the backup period of stage 1 and 2.
Previous studies have shown that as much as 8\% or even more of total capacity must be reserved for
CoW \cite{EMCIncrementalDataChanges}, while the actual cost of CoW is a factor of the
data size, the write rate, and duration of CoW protection.
The second problem is that a single round backup brings the highest cost of CoW
because of the workload in stage 1a is imbalanced (see Fig.~\ref{fig:hist-1}),
causing machines with small VMs to wait while CoW protection is turned on.
Thus we must minimize the duration that a given VM is undergoing CoW protection.r

To determine how evenly distributed VM sizes are, we obtained statistical data
for 22 Aliyun clusters. The clusters in our dataset all have a very long tail distribution,
Though local minima exist in the histogram and the range of VM sizes varies. Other production clusters
may have different distributions, but our findings justify our architecture for a multi-round algorithm.
A representative histogram for one of the clusters is shown in Fig.~\ref{fig:hist-1}.

\begin{figure}[ht]
  \centering
  \begin{tikzpicture}
      \begin{axis}[
              ybar interval,
      ]
          \addplot+[hist={bins=10}] table[y=AY41G] {figures/cluster_distributions.txt};
      \end{axis}
  \end{tikzpicture}
  \caption{Histogram of average data sizes for a real cluster. TODO:reformat graph, I just wanted to get the data into the paper}
  \label{fig:hist-1}
\end{figure}
